### 2019-03-02 manuscript/results.tex
Major introduction changes, main figure changes and revised methods

% NOTE: will need to update figure/panel refs if making no-delta models primary

@@

Evolution from SI diploids to SC polyploids can proceed through two different pathways.
Determining the relative contribution of these pathways based on our estimated transition rates from the ID/CD/CP model, we find that the one-step pathway is more likely on short timescales and the two-step pathway is more likely on long timescales (\cref{figure:pathways}, left panels).
When not much time has elapsed, the one-step pathway is more likely because only one event need happen.
When more time has elapsed, the two-step pathway is more likely because the rate of loss of SI within diploids, $q_{IC}$, is greater than the rate of polyploidization for SI species, $\rho_I$ (\cref{suppfigure:IDCDCPnodip}).
These conclusions are the same as those of \citet{robertson_2011} under one of their branch length approximations.

@@

\begin{figure}
\includegraphics[width=\textwidth]{Netdiversificationallmodels.pdf} % FIXME: The panel labels should use "+A/B" instead of "-A/B".  Rosana, if you add the .svg file for this figure, I can make small changes like this.
\caption{Net diversification rates for all models that include diploidization.}  
\label{figure:netdivall}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{netdiversificationallnodip.pdf} % FIXME: same note as above about "+A/B"
\caption{Net diversification rates for all models that do not include diploidization.}  
\label{figure:netdivnodip}
\end{figure}

@@

\begin{suppfigure}
\includegraphics[width=\textwidth]{bisseDPposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the D/P, polyploidy model} % XXX
\label{suppfigure:DP}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{bisseDPnodipposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the D/P no $\delta$, polyploidy model} % XXX
\label{suppfigure:DPnodip}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{hisseDPposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the D/P+A/B, polyploidy model.  The axis is offset in one location so that the two overlapping distributions can be seen.} % XXX
\label{suppfigure:DPAB}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{hisseDPnodipposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the D/P no $\delta$+A/B, polyploidy model} % XXX
\label{suppfigure:DPnodipAB}
\end{suppfigure}

@@

\begin{suppfigure}
\includegraphics[width=\textwidth]{musseDPSIposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the ID/CD/CP, polyploidy and breeding system model} % XXX
\label{suppfigure:IDCDCP}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{musseDPSInodipposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the ID/CD/CP no $\delta$, polyploidy and breeding system model} % XXX
\label{suppfigure:IDCDCPnodip}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{muhisseDPSIposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the ID/CD/CP+A/B, polyploidy and breeding system model} % XXX
\label{suppfigure:IDCDCPAB}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{muhisseDPSInodipposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the ID/CD/CP no $\delta$+A/B polyploidy and breeding system model} % XXX
\label{suppfigure:IDCDCPnodipAB}
\end{suppfigure}

>>>>

% NOTE: will need to update figure/panel refs if making no-delta models primary
% R: I am changing no delta as just D/P and prevous D/P as +delta

@@

Evolution from self-incompatible diploids to self-compatible polyploids can proceed through two different pathways.
Determining the relative contribution of these pathways based on our estimated transition rates from the ID/CD/CP model, we find that the one-step pathway is more likely on short timescales and the two-step pathway is more likely on long timescales (\cref{figure:pathways}, left panels).
When not much time has elapsed, the one-step pathway is more likely because only one event need happen.
When more time has elapsed, the two-step pathway is more likely because the rate of loss of SI within diploids, $q_{IC}$, is greater than the rate of polyploidization for SI species, $\rho_I$ (\cref{suppfigure:IDCDCPnodip}).
These conclusions are the same as those of \citet{robertson_2011} under one of their branch length approximations.

@@

\begin{figure}
\includegraphics[width=\textwidth]{allnetdivmodelswithoutdelta.pdf} % FIXME: The panel labels should use "+A/B" instead of "-A/B".  Rosana, if you add the .svg file for this figure, I can make small changes like this.
\caption{Net diversification rates for all models.}  
\label{figure:netdivall}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{allnetdivmodelsdiploidization.pdf} % FIXME: same note as above about "+A/B"
\caption{Net diversification rates for all models that include diploidization.}  
\label{figure:netdivnodip}
\end{figure}

@@

\begin{suppfigure}
\includegraphics[width=\textwidth]{bisseDPnodipposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the D/P, polyploidy model} % XXX
\label{suppfigure:DPnodip}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{bisseDPposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the D/P+ $\delta$,polyploidy model} % XXX
\label{suppfigure:DP}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{hisseDPnodipposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the D/P+A/B, polyploidy model} % XXX
\label{suppfigure:DPnodipAB}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{hisseDPposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the D/P+$\delta$+A/B, polyploidy model.  The axis is offset in one location so that the two overlapping distributions can be seen.} % XXX
\label{suppfigure:DPAB}
\end{suppfigure}

@@

\begin{suppfigure}
\includegraphics[width=\textwidth]{musseDPSInodipposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the ID/CD/CP, polyploidy and breeding system model} % XXX
\label{suppfigure:IDCDCPnodip}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{musseDPSIposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the ID/CD/CP+$\delta$, polyploidy and breeding system model} % XXX
\label{suppfigure:IDCDCP}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{muhisseDPSInodipposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the ID/CD/CP+A/B polyploidy and breeding system model} % XXX
\label{suppfigure:IDCDCPnodipAB}
\end{suppfigure}

\begin{suppfigure}
\includegraphics[width=\textwidth]{muhisseDPSIposteriordist.pdf}
\caption{Posterior distribution for each of the parameters in the ID/CD/CP+$\delta$+A/B, polyploidy and breeding system model} % XXX
\label{suppfigure:IDCDCPAB}
\end{suppfigure}
